### 2023-10-28 appendices/appendixA.tex
corrected results

This is the circuit that comes after the voltage multiplier (section \ref{sec:models}), it is here to amplify the results of the voltage multiplier by 10. Sometimes, its use doubles as an adder making it an inverting summing amplifier (TODO circuit).

@@

Some versions of the hard sigmoid are a bit different from \cref{eq:hSigmoid}, the slope depends on the library used \cite{hSigmoid1}.

@@

>>>>

This is the circuit that comes after the voltage multiplier (\cref{sec:models}), it is here to amplify the results of the voltage multiplier by 10. Sometimes, its use doubles as an adder making it an inverting summing amplifier (TODO circuit).

@@

Some versions of the hard sigmoid are defined differently from \cref{eq:hSigmoid}, the slope depends on the library used \cite{hSigmoid1}.

@@

\section{Smoothing the curve}\label{apsec:smoothFunc}

\begin{lstlisting}[language=Python]
Put your code here.
\end{lstlisting}

### 2023-10-28 results/airline.tex
corrected results

Interestingly, the results look much better when using the \ac{GRU} layer. The error rate confirms that as it is almost half of what it was with the \ac{LSTM} layer (\cref{tab:airlineDigital}). That simply means that the \ac{GRU} layer is better at handling this problem, as was previously stated in \cref{sec:gru}.

@@

This subsection shows the importance of using the analog activation functions in the training phase of the \ac{NN}.

The \ac{LSTM} layer being the only to have been trained using the default activation functions the only results presented here are using an \ac{LSTM} layer.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\linewidth]{results/airline/noCustomAFZoomed}
  \caption{Analog predictions trained with the default activation functions.}
  \label{graph:airlineAnalogNoCZoomed}
\end{figure}

@@

This similarity is further proven by the errors shown in \cref{tab:airlineAnalogNoCZoomed}. Those error are all around four thousands passengers, which is negligible in our case. That shows a certain stability of the system when using different values of serial size ($n_s$). The error rate is also quite low because of the lower results obtained.

@@

\Cref{tab:airlineAnalog} contains the errors of the analog predictions. It shows that, as can be observed, the results the closest to the target are the ones generated using a serial size of one ($n_s=1$). Indeed, its error ($28.41$) is lower than the error from the digital results ($52.27$) to the original target values, almost half of it. The other ones are still very close to the targeted curve, but are still lower. This is probably due to the serialization circuit causing small differences in the signals at each steps.

@@

Once again, the results are quite close to each others, but as expected the errors (\cref{tab:airlineAnalogError}) are higher then the ones found in \cref{tab:airlineAnalogNoCZoomed}. The farthest appart ($n_s=1$ to $n_s=2$ with an error of $64.6$ thousands passengers) have an error barely higher than the error of digital results to the target dataset (\cref{tab:airlineDigital})

coincidentally, the curve is closer to the target curve than the digital prediction itself, this is mostly due to the lack of precision of the analog prediction, but it is nevertheless interresting to mention. \Cref{graph:airlineCoin} shows the graph and the \ac{RMSE} is the lowest, even lower than the ones from the digital predictions.

\begin{figure}[H]
  \centering
  \includesvg[width=\linewidth]{results/airline/closeRes}
  \caption{Analog prediction ($n_s=1$) with the target dataset.}
  \label{graph:airlineCoin}
\end{figure}

The overall observation of those results compared to the previous ones (\cref{subsec:airlineAnalogNoC}) are how much closer to their target they are. It still is not quite perfect but simply changing the activation functions used for training improved the results by a lot. It can thus be theorized that the error will become null if the system is trained with the same parameters as the ones it is using for inference. In other words, the error will probably be nullified when the training will happen inSitu (\cref{subsec:inSitu}).

>>>>

Interestingly, the results look much better when using the \ac{GRU} layer. The error rate of $36,6$ confirms that as it is almost half of what it was with the \ac{LSTM} layer (\cref{tab:airlineDigital}). That simply means that the \ac{GRU} layer is better at handling this problem, as was previously stated in \cref{sec:gru}.

@@

This subsection shows the importance of using the analog activation functions in the training phase of the \ac{NN}. The \ac{LSTM} layer being the only to have been trained using the default activation functions the only results presented here are using an \ac{LSTM} layer.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\linewidth]{results/airline/noCustomAFZoomed}
  \caption{Analog predictions trained with the default activation functions zoomed on the the analog predictions.}
  \label{graph:airlineAnalogNoCZoomed}
\end{figure}

@@

This similarity is further proven by the errors shown in \cref{tab:airlineAnalogNoCZoomed}. The erros are $3.97$, $4.78$ and $5.05$. Those error are all around four thousands passengers, which is negligible in our case. That shows a certain stability of the system when using different values of serial size ($n_s$). The error rate is also quite low because of the lower results obtained.

@@

\Cref{tab:airlineAnalog} contains the errors of the analog predictions. It shows that, as can be observed, the results the closest to the target are the ones generated using a serial size of one ($n_s=1$). Indeed, its error ($28.4$) is lower than the error from the digital results ($52.3$) to the original target values, almost half of it. The other ones are still very close to the targeted curve, but are still lower. The errors are higher when running the system in serial mode. This higher inaccuracy is probably due to the data staying for longer in the memory cells as the time steps get longer.

@@

Once again, the results are quite close to each others, but as expected the errors (\cref{tab:airlineAnalogError}) are higher then the ones found in \cref{tab:airlineAnalogNoCZoomed}. This is due to the fact that the errors depend on the scale of the results, the predcitions here having a much greater range (\cref{tab:airlineAnalog}). The farthest appart ($n_s=1$ to $n_s=2$ with an error of $64.6$ thousands passengers) have an error barely higher than the error of digital results to the target dataset (\cref{tab:airlineDigital})

The overall observation of those results compared to the previous ones (\cref{subsec:airlineAnalogNoC}) are how much closer to their target they are. It still is not quite perfect but simply changing the activation functions used for training improved the results by a lot. It can thus be theorized that the error will greatly decrease if the circuit is trained with the same parameters as the ones it is using for inference. In other words, the error will probably be very low when the training will happen inSitu (\cref{subsec:inSitu}).

### 2023-10-28 results/celegans.tex
corrected results

It has been established in \cref{sec:resAirline}, that the analog circuit with a serial size of one ($n_s=1$) show a lower \ac{RMSE} to the digital predictions than the digital predictions.

@@

\Cref{graph:celegansAnalog0} contains the predictions of both the digital and analog \ac{NN} for all four output neurons that are being monitored. The having all predicted responses to the stimuli on the same graph makes things very unintelligeable.

@@

The data is not useless for that matter. It was decided to smooth the data by averaging every output point with its neighboring points. This simple average will smooth out the curves to get a decently readable result, that can then be compared with the digitally predicted response. The python code for this function is available at \cref{}. %TODO

@@

The \cref{bar:rmse5} shows that adjusted or not, the errors are in the expected range. Adjusting the results reduces the error a bit, mainly due to the sliding of the results. Smoothing out the curve does not affect the error as it simply does a local average of each value. The erros are, once again higher when obtained with the analog simulation than with the digital inference.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\linewidth]{results/celegans/out15}
  \caption{\acs{C. elegans} analog responses with their digital counterparts}
  \label{graph:celegansAnalog0}
\end{figure}

\Cref{graph:celegansAnalog0} contains the predictions of both the digital and analog \ac{NN} for all four output neurons that are being monitored. The having all predicted responses to the stimuli on the same graph makes things very unintelligeable.

>>>>

It has been established in \cref{sec:resAirline}, that the analog circuit with a serial size of one ($n_s=1$) shows a lower \ac{RMSE} to the digital predictions than the digital predictions.

@@

\Cref{graph:celegansAnalog0} contains the predictions of both the digital and analog \ac{NN} for all four output neurons that are being monitored. \Cref{graph:celegansAnalog0} having all predicted responses to the stimuli on the same graph makes things very unintelligeable.

@@

The data is not useless for that matter. It was decided to smooth the data by averaging every output point with its neighboring points. This simple average will smooth out the curves to get a decently readable result, that can then be compared with the digitally predicted response. The python code for this function is available in \cref{apsec:smoothFunc}.

@@

The \cref{bar:rmse5} shows that adjusted or not, the errors are in the expected range. Adjusting the results slightly reduces the error, mainly due to the sliding of the results. Smoothing out the curve does not affect the error as it simply does a local average of each value. The erros are, once again higher when obtained with the analog simulation than with the digital inference.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\linewidth]{results/celegans/out15}
  \caption{\acs{C. elegans} analog responses with their digital counterparts}
  \label{graph:celegansAnalog1}
\end{figure}

\Cref{graph:celegansAnalog1} contains the predictions of both the digital and analog \ac{NN} for all four output neurons that are being monitored. For the reasons mentioned in the previous section, for the sake of readability, the predictions are spread out on separate graphs.
